%-------------------------
% Date: 2023-03-01
% Author: Ignacio Gaitan
%-------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

% Adjust section formatting
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip}

% Define custom bullet for itemize
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine-readable/ATS-parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \textit{\small#5} & \textit{\small #6} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeCertificationHeading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\small #2} \\
    \textit{\small#3}
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\LARGE Ignacio Gaitán} \\ \vspace{2ex}
    \textit{Artificial Intelligence - Senior Machine Learning Computer Vision Engineer} \\ \vspace{2ex}
    \small
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/ignacio-gaitan}{LinkedIn}
    $|$
    \faAt \hspace{.5pt} \href{mailto:gaitan.ignacio@icloud.com}{gaitan.ignacio@icloud.com}
    $|$
    \faMobile \hspace{.5pt} \href{tel:+59895501231}{(+598) 95 501 231}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/gaitanignacio}{GitHub}
    $|$
    \faGithub \hspace{.5pt} \href{https://gitlab.com/gaitan.ignacio}{Gitlab}
    %$|$
    %\faGlobe \hspace{.5pt} \href{https://gaitanignacio.github.io}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Prof.+Juan+Carlos+Sabat+Pebet+1234,+11300+Montevideo,+Departamento+de+Montevideo,+Uruguay/@-34.9044985,-56.1366609,17z/data=!3m1!4b1!4m6!3m5!1s0x959f813e56b3cedd:0x5a415e79543b2770!8m2!3d-34.9044985!4d-56.134086!16s%2Fg%2F11pysbccyt?entry=ttu}{Montevideo, Uruguay}
\end{center}

\vspace{-2ex}

\section*{Summary}
I hold a bachelor's degree in Electrical Engineering and completed postgraduate studies in Tech Business Management. 
Currently, I work as a Senior Machine Learning Engineer at Disney Parks as a contractor through Globant. 
I have over ten years of experience in roles related to technology in both corporate and academic settings, with four years of experience in teaching at universities. 
I am a proactive, determined professional with a passion for challenges and excellent analytical and communication skills. 
Proficient in Python, C++, and ROS, I have extensive experience in artificial intelligence. 
I have a proven track record in designing, leading, and implementing peta-scale artificial intelligence and machine learning applications and solutions. 
Currently seeking opportunities to contribute in the field of machine learning engineering and/or robotics.

\section*{Skills}
    \vspace{2pt}
    \resumeSubHeadingListStart
        \small{\item{
            \textbf{Programming:}{ Python, Flask, FastAPI, C++, ROS, MATLAB, R, Git, SQL, MySQL, NoSQL}  \\ \vspace{3pt} % SQLServer, MongoDB
            \textbf{Cloud and Infra:}{ AWS, Serverless, SageMaker, MLOps, S3, EC2, Kubernetes, Docker, Edge Computing}  \\ \vspace{3pt}
            \textbf{Computer Vision:}{ Object detection, instance/semantic segmentation, feature extraction, object tracking}  \\ \vspace{3pt}
            \textbf{Machine Learning:}{ Deep learning, Neural networks, OpenCV, TensorFlow, PyTorch, CUDA}  \\ \vspace{3pt}
            \textbf{Robotics:}{ Robot Operating System (ROS), motion planning, control systems}  \\ \vspace{3pt}
            \textbf{Soft Skills:}{ Team player, inspiring others to cooperate by displaying credibility and confidence. Listen attentively, using tact and diplomacy to find common ground and achieve win-win outcomes. Effective organizing, assembling and arranging resources to meet goals.} \\ \vspace{3pt}
        }}
    \resumeSubHeadingListEnd
\section*{Professional Experience}
    \vspace{3pt}
    \resumeSubHeadingListStart  
        \resumeSubheading
            {The Walt Disney Company}{Orlando, Florida, United States (Remote contractor))}
            {Artificial Intelligence - Senior ML Computer Vision Engineer}{Dec 2020 \textbf{--} Present, Full-time}
            \resumeItemListStart
                \resumeItem{Led, researched \& developed of highly scalable (1MM req/day) artificial intelligence cloud solutions.}
                \resumeItem{Developed fault tolerant and fully serverless software applications in the fields of machine and deep learning specially in the computer visions area.}
                \resumeItem{Developed computer vision algorithms to enhance photo capture experiences at Disney parks.}
                \resumeItem{Trained and fine tuned machine learning models for image recognition and object tracking.}
                \resumeItem{Collaborated with cross-functional teams to develop image active learning data pipelines to train models on various computer vision tasks such as instance segmentation, skeleton keypoint detection, and object detection.}
                \resumeItem{Developed ROS noetic serverless service for automating image data collection and posterior annotation in theme park environments.}
            \resumeItemListEnd

        \resumeSubheading
            {CUTI - Chamber of Uruguayan Tech Companies}{Montevideo, Uruguay}
            {Tech Mentor @ Sembrando TIC program}{Apr 2021 \textbf{--} Dec 2021, Full-time}
            \resumeItemListStart
                \resumeItem{Mentored a group of more that 30 young people in the Sembrando TIC program, which aims to increase opportunities for those who come from vulnerable socioeconomic backgrounds to enter the Tech industry.}
            \resumeItemListEnd

        \resumeSubheading
            {Marvik AI}{Montevideo, Uruguay}
            {Artificial Intelligence - Sr. Data Scientist}{Sep 2019 \textbf{--} Dec 2020, Full-time}
            \resumeItemListStart
                \resumeItem{Senior Data Scientist at an artificial intelligence software development company that delivers innovative solutions for customers' business needs.}
                \resumeItem{Lead research \& development of artifitial intelligence software applications to satisfy customers needs in the fields of computer vision, natural language processing and predictive analytics.}
            \resumeItemListEnd

        \resumeSubheading
            {Telefónica Móviles del Uruguay}{Montevideo, Uruguay}
            {Machine Learning and Business Intelligence Analyst}{Dec 2016 \textbf{--} Sep 2019, Full-time}
            \resumeItemListStart
                \resumeItem{Developed advanced analytical solutions and data science products and applications for sales forcasting, default prediction, among others.}
                \resumeItem{Participated in the data governance decisions of the commercial department, report automation, ETL development and DataMart design and management.}
                \resumeItem{Responsible for analyzing data to support decision-making, development of advanced analytical solutions, tools, and data science applications.}
                % \resumeItem{Initially in charge of data governance of the commercial department, report automation, ETL development, DataMart design, and management, as well as the development of dashboards and reports for business monitoring and drawing conclusions.}
            \resumeItemListEnd

        \resumeSubheading
            {Universidad Católica del Uruguay}{Montevideo, Uruguay}
            {Professor - Engineering and Technology School}{Mar 2014 \textbf{--} Feb 2017, Part-time}
            \resumeItemListStart
                \resumeItem{Taught various specific sciences in the Faculty of Engineering and Technologies, including Electrical Circuits, Electrical Circuits Laboratory, Physics II Laboratory, and Physics I Laboratory.}
            \resumeItemListEnd

        \resumeSubheading
            {Isbel S.A}{Montevideo, Uruguay}
            {Telcos Presales Engineer \& Key Account Manager}{Nov 2011 \textbf{--} Sep 2016, Full-time}
            \resumeItemListStart
                \resumeItem{ Responsible for the commercial development of corporate accounts in the private sector.}
                \resumeItem{Sold solutions for different kinds of technologies, including Business Intelligence, Networking, Telephony, Infraestructure, and Security.}
                \resumeItem{Responsible for managing the sales process with telecommunications customers, conducting technical presales for tailored solutions, and analyzing and implementing telecommunication projects for operators in Uruguay.}
                \resumeItem{Strengthened long-term relationships with customers and suppliers to promote "win-win" relationships.}
            \resumeItemListEnd
    
    \resumeSubHeadingListEnd

\section*{Education}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \resumeEducationHeading
            {Universidad de la República, Economics Science School}{Montevideo, Uruguay}
            {Postgraduate in Business Management of Tech companies; \textbf{GPA: 3.81/5.00}}{Mar 2017 \textbf{--} Dec 2017}
            {}{}

        \resumeEducationHeading
            {Universidad Católica del Uruguay}{Montevideo, Uruguay}
            {B.Sc. in Electrical and Electronics Engineering; \textbf{GPA: 3.81/5.00}}{Mar 2010 \textbf{--} Dec 2014}
            {Minor Degree in Telecomunications; \textbf{GPA: 3.81/5.00}}{Mar 2015 \textbf{--} Dec 2015}
    \resumeSubHeadingListEnd

\section*{Awards \& Achievements}
    \vspace{3pt}
    \resumeSubHeadingListStart
      \small{\item{
          \textbf{Scholarship for Academic Excellence:}{ Received a full payment scholarship for academic excellence from the Universidad Católica del Uruguay, a scholarship with a highly competitive 5\% admission rate. (Dec 2009)} \\ \vspace{3pt}
  
          \textbf{Bachelor's Graduates Ranking:}{ Earned the second-highest grade among fellow graduates in the bachelor's degree program. (Dec 2015)} \\ \vspace{3pt}
      }}
    \resumeSubHeadingListEnd

\section*{Notable Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
        % (TODO) ADD MISSING PROJECTS
        \resumeProjectHeading
            {\textbf{Luisa ROS2 Robotics Project} $|$ \emph{\href{https://gitlab.com/gaitan.ignacio/luisa-robot}{\color{blue}Gitlab}}}{Aug 2023}
            \resumeItemListStart
                \resumeItem{In-progreess development of an advanced humanoid robot equipped with various hardware components, capable of performing human-like tasks.
                Integrated computer vision algorithms with ROS2 to perform object detection and tracking and natural language processing algorithms and ROS2 services to perform speech recognition and text-to-speech.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Active Learning Data Pipeline}}{Mar 2023}
            \resumeItemListStart
                \resumeItem{Led cloud developement of an active learning pipeline for training neural networks on various computer vision tasks such as instance segmentation, skeleton keypoint detection, and object detection.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Automatic image moderation system}}{Oct 2021}
            \resumeItemListStart
                \resumeItem{Developed a computer vision algorithm and serverless system to detect and moderate inappropriate images capable of processsing more than 1MM requests per day.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Computer Vision for tracking People in Retail Store}}{Aug 2020}
            \resumeItemListStart
                \resumeItem{Developed a computer vision algorithm to track people in a retail store and count the number of people in the store at any given time.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Computer Vision and Edge Computing Project for Mining Safety}}{Mar 2020}
            \resumeItemListStart
                \resumeItem{Implemented IoT deep learning image classification in real-time to identify truck drivers' behaviors and send alerts to a central API if the conduct was not safe while driving.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Computer Vision for Aging People’s faces}}{Sep 2019}
            \resumeItemListStart
            \resumeItem{Developed a microservice for aging people's faces leveraging StyleGAN and custom-trained models to identify the age direction in the latent space.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{Default prediction}}{Sep 2017}
            \resumeItemListStart
                \resumeItem{Developed a machine learning model and service to predict the probability of default of a customer when receiving a loan. Being able to reduce the default rate by 50\%.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd

\section*{Certifications}
    \vspace{3pt}
    \resumeSubHeadingListStart
        % (TODO) ADD MISSING CERTIFICATIONS SPECIFICALLY ROS ONES @ UDEMY
        \resumeCertificationHeading
        {Synergic Partners}{Aug 2018}{Data Engineering Program - Big Data} \\ \vspace{3pt}
        \resumeCertificationHeading
        {DataCamp}{Jul 2018}{\href{https://www.datacamp.com/statement-of-accomplishment/course/570aea98df0efb32a187e8827252a6e45461ef1f}{Credit Risk Modeling in R}} \\ \vspace{3pt}
        \resumeCertificationHeading
        {Coursera | University of Washington}{May 2018}{\href{https://www.coursera.org/account/accomplishments/verify/Q6FA9BCRNPDD}{Communicating Data Science Results}} \\ \vspace{3pt}
        \resumeCertificationHeading
        {Coursera | University of Washington}{May 2018}{\href{https://www.coursera.org/account/accomplishments/verify/AWPU7U793JRS}{Practical Predictive Analytics: Models and Methods}} \\ \vspace{3pt}
        \resumeCertificationHeading
        {Coursera | University of Washington}{May 2018}{\href{https://www.coursera.org/account/accomplishments/verify/QRZJQH9JU9XW}{Data Manipulation at Scale: Systems and Algorithms}} \\ \vspace{3pt}
        \resumeCertificationHeading
        {Database Management}{Aug 2015}{Coursera specialization by Universty of Colorado.} \\ \vspace{3pt}
        % Data Science at Scale - Capstone Project 2018 by University of Washington
        % Data Warehousing for Business Intelligence Specialization, University of Colorado System.
    \resumeSubHeadingListEnd

\section*{Languages}
    \vspace{3pt}
    \resumeSubHeadingListStart
        \small{\item{
            \textbf{English:}{ Upper Intermediate (Professional Working)} \\ \vspace{3pt}
            \textbf{Spanish:}{ Fluent (Native)} \\ \vspace{3pt}
        }}
    \resumeSubHeadingListEnd

\end{document}
